%!TEX encoding = UTF-8 Unicode
% !TeX spellcheck = en_GB
\chapter{Conclusion}
Constraints on Higgs observables are deeply intertwined with top and flavour physics. This has been highlighted throughout the entirety of this thesis, and the literature reviewed within. \\  The era of Higgs precision measurements  is on the horizon, prompting the inclusion of Higher order corrections to Higgs processes, which requires improved techniques for their calculation. An example of these techniques is the $\pt$ expansion, first employed to obtain an analytic form for the Higgs pair virtual corrections~\cite{Bonciani:2018omm}. This techniques was used in~\autoref{chap:hz}, for obtaining the QCD two-loop corrections of the gluon fusion component of $Zh$, which is the main source of this process's theoretical uncertainty. The true power of this method is seen when combined with Pad\'e approximants to bridge it with other expansions in order to obtain an analytic form for the virtual corrections covering the entire invariant mass spectrum~\cite{Bellafronte:2022jmo}. \\ The use of higher-order calculations in SMEFT opened the potential for probing the Higgs trilinear self-coupling~\cite{Gorbahn:2016uoy, Degrassi:2016wml, Bizon:2016wgr, Maltoni:2017ims, Degrassi:2021uik}, and show connections between four-top operators and EWPO~\cite{Dawson:2022bxd}. The nexus between the SMEFT four-heavy quark operators and the Higgs self-coupling is explored in~\autoref{chap:4topSingleHiggs}, via the inclusion of NLO SMEFT effects in single-Higgs rates. \\ Precision Higgs measurements will not be complete without the observation of Higgs pair production, the aspired jewel process of the HL-LHC, which carries the most potential for measuring the elusive Higgs self-coupling,  consequently revealing the shape of the Higgs potential.\\ In~\autoref{chap:lightyuk}, we have demonstrated the potential of this process in constraining other ``difficult'' Higgs observable; its interaction  with the light quarks. Then, we proceeded to treating Higgs pair production as a multivariate problem and employed aspects of Interpretable machine learning~\cite{Grojean:2020ech}. Using a BDT-classifier interfaced with Shapley values as an interpretability layer, we were able to constrain the trilinear coupling along with the up- and down-quarks Yukawa coupling enhancements, within SMEFT. The interpretability allowed for optimised classifier as well as added physics understanding and confidence. The constraints project for HL-LHC on up-quark  Yukawa coupling enhancement obtained from this analysis is the most stringent amongst the proposed channels.  \\ The harmony of amongst different observables within SMEFT framework extends towards the newly-discovered flavour anomalies involving $ b \to s \ell \ell$ transitions, which was explored in~\autoref{chap:flav}. When these anomalies are confronted with EWPO, a marked tension of up to $ 6\sigma$ is observed between the data from $B$ decays and EWPO, further highlighting the interplay between these anomalies and EWPO~\cite{Bhattacharya:2014wla,Feruglio:2016gvd,Celis:2017doq,Buttazzo:2017ixm,Kumar:2018kmr,Ciuchini:2019usw,Aebischer:2019mlg,Cornella:2019hct}.\\ This conundrum can be resolved by a global fit involving EW and flavour data. A minimalist SMEFT model, assuming no new flavour spurions involved would generate LUV at loop-level, and involves operators from the top and Higgs sectors. We have later showcased UV-complete models ascertained from this fit to explain these flavour anomalies. The first model was based on $Z^\prime$ models with top-partner VLQ~\cite{Kamenik:2017tnu}, while the other is a set of top-phillic leptoquark models. \\ Although there is not clear direction for BSM physics hinted by current  LHC data, the SMEFT offers a versatile anatomy for new physics searches, with minimal assumptions on its degrees of freedom. More importantly, the correlations seen within SMEFT operators from different sectors could be as a starting point from data-driven model building, after all, physics is .. an \emph{experimental science !}